The responses of \textit{Spinifex littoreus} to sand burial on the coastal area of Pingtan Island, Fujian Province, South China

### 2020-12-13 tex/interactcsesample.tex
re-write results section

\subsection{Influence of sand burial on the biomass allocation}

>>>>

\begin{figure}[!h]
  \centering
  \includegraphics[scale=0.8]{../figs/grid_differences.jpg}
  \caption{
    % 不同沙埋处理下，植株的株高生长（A）与匍匐茎生长（B）同空白对照组之间的差异变化。
    Difference in ramets height growth (\textbf{A}) and horizontal stolons (\textbf{B}) between control group (CG) and different sand burial treatments. The blue dots refer negative (less than CG) while the red dots refer positive (larger than CG) differences. The fulfilled dots are significant different in statistic ($P<0.05$) and size of the dots denotes the size of difference.  
  } 
  \label{fig:lattice}
\end{figure}

\begin{figure}[!h]
  \centering
  \includegraphics[scale=0.8]{../figs/growth_process.jpg}
  \caption{
    Growth process of horizontal stolons with half intense (HI) group and complete intense (CI) group plants.
    \textbf{A} growth of horizontal stolons' length of HI group, compared with the control group (CG).
    \textbf{B} growth of horizontal stolons' length of CI group, compared with the control group (CG).
    \textbf{C} growth of different sections of horizontal stolons' length of HI group.
    \textbf{D} growth of different sections of horizontal stolons' length of CI group.
  }
  \label{fig:growth}
\end{figure}

% 不同的沙埋处理下的老鼠楽株高的生长过程与空白对照之间没有显著差异（图1A），但沙埋对老鼠楽匍匐茎的伸长生长产生了显著影响（图1B）。
With different treatments, there was no significant difference between the growth of ramets height, but with significant effects on the growth of horizontal stolons when intense half sand burial (HI) and complete intense sand burial (CI) (Figure~\ref{fig:lattice}).
While the significant effect of CI occurred after 9 days after sand burial treatment, the significant effect of a HI group occurred at 13 days and 20 days after sand burial. 
% CI组不仅时间效应出现的更早，而且对水平stolons生长的促进作用也大于HI组，在20天砂埋试验结束时，其stolons长度显著增加24.56\%和40.79\%。
Not only did the time effect appear earlier with the CI group, but also had a greater promoting effect on the growth of horizontal stolons than the HI group, with significant increases in stolons' length of 40.79\% and 24.56\% respectively at the end of 20-day sand burial experiment (Figure~\ref{fig:growth} A and B).
% 其伸长生长过程都在不断增加顶端1/3长度所占的比例，而基部长度占比和中段的长度占比均匀下降（图2C-D）。
During the elongation growth process, the proportion of the length of the top 1/3 (apex) increased continuously, while the proportion of the length of the base and the length of the middle sections decreased uniformly (Figure~\ref{fig:growth} C and D).

\subsection{Influence of sand burial on the biomass allocation}
\begin{figure}
  \centering
  \includegraphics[scale=0.6]{../figs/roots.jpg}
  \caption{
    \textbf{A.} Total length of adventitious roots under different sand burial treatments.
    \textbf{B.} Number of adventitious roots under different sand burial treatments.
    \textbf{C.} Mean dry weights in different sections of horizontal stolons.
  }
  \label{fig:roots}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[scale=0.8]{../figs/ratio.jpg}
  \caption{
    Ratio between stem weights and leaf weights after the experiments under different treatments. The white lines denote mean ratio of the control group (CG) while the grey spans denote the standard error of. Weights ratio from different sections were compared one by one (\textbf{A:} base sections, \textbf{B:} middle sections, \textbf{C:} apex sections, \textbf{D:} all sections).
  }
  \label{fig:ratio}
\end{figure}

% 大多数的人工沙埋不同程度上促进了不定根的生成，无论是不定根数量还是总长度（Fig3）。
Most of sand-burial treatments promote the generation of adventitious roots to varying degrees, both in terms of the number of roots and the total length of the roots (Figure~\ref{fig:roots} A and B).
% 而且不定根主要分布在基部，顶端无不定根生成。
What's more, the adventitious roots are mainly distributed at the base and the adventitious roots are not generated at the apex (Figure~\ref{fig:roots} C).
% 经过20天的沙埋实验，老鼠楽植株茎和叶片的干重比例在不同程度上发生了改变。
After 20 days of sand-burying experiments, the ratio of dry weight between stems and leaves of \textit{S. littoreus} plant changed to varying degrees (most of which decreased in ratio of stem weight and leaf weight) under different treatments (Figure~\ref{fig:ratio}).
% 相对于空白对照组来说，沙埋使得植株将干重更多分配在茎上而非叶片上，在植株的顶端尤其明显。
Compared with the control group (CG), sand burial caused the plant to distribute dry weight more on the stem than on the leaves, especially at the top of the plant (Figure~\ref{fig:ratio} C).
